---
title: "R package developement"
author: "Junzhe Shao"
date: "10/21/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Credit to John Muschelli  
## Where to start

check your name is available on CRAN, Bioconductor or GitHub
```{r eval=FALSE}
library(available)
available("ssmimputedemo")
```
## Basic file Introduction in R package:

~/man/xx.Rd ...... R documentation  
~/DESCRIPTION .......  
sample description file:  
Package: ssmimputedemo  
Type: Package  
Title: SSM Imputation DEMO(Title Case)  
Version: 0.1.0  
Author: Junzhe Shao  
Maintainer: The package maintainer <yourself@somewhere.net>  
Description: More about what it does (maybe more than one line)  
    Use four spaces when indenting paragraphs within the Description.  
    A demo for SSM Imputation  
License: GPL-3  
Encoding: UTF-8  
LazyData: true  
  
Build -> install and restart  
```{r}
library(ssmimputedemo)
?hello
```
## Roxygen
  
Build -> Configure Build Tools -> Build Tools  
Configure Roxygen -> Check everything  
cran check : --as-cran to be more stable  
  
roxygen file automatically create .Rd file any time we recompile the package  
  
Code ->insert roxygen skeleton  
```{r eval=FALSE}
#' @title 
#' @description 
#' My hello world function
#' @param x The name of person to say hi to
#'
#' @return The output from  \code{\link{print}}    
#' @export
#'
#' @examples
#' hello("Steve")
#' \dontrun{
#' hello("Steve")}
```
  
tab auto completion for @__,`r #' My hello world function` will create title and description exactly the same.
\code{\link{print}}can link you to outside, examples and \dontrun{}function
  
Build -> clean and rebuild
  
ℹ Loading ssmimputedemo
Warning: The existing 'hello.Rd' file was not generated by roxygen2, and will not be overwritten.
Warning: The existing 'NAMESPACE' file was not generated by roxygen2, and will not be overwritten.
  
delete these files with default setup
Build -> clean and rebuild
  
export(hello), let the users using hello
check package
  
creater a new printer funtion, you can add multiple files
 
## R package usethis
```{r eval=FALSE}
library(usethis)
#automaticlly create a readme file
use_readme_rmd()
#push to github, set github remote repository
use_git(message = "")
use_github(protocol = "https")
```
  
really nice to add these
RoxygenNote: 7.1.2  
URL: https://github.com/Junzheshao5959/ssmimputedemo  
BugReports: https://github.com/Junzheshao5959/ssmimputedemo/issues  


Importing and Exporting funcitons
